Open-Source machine learning BANTER acoustic classification of a cryptic echolocating species

### 2022-12-14 manuscript/manuscript.qmd
Add Hawaii Dataset
Run Hawaii Dataset. Gitignore should include the binaries/database folders in the Hawaii folder dataset

@@

      name: Journal Name

@@

      model: 3p

@@

\[Insert Figure 2\]\[Figure 2. BANTER classification results from the SAtlantic dataset. Confusion matrix (a) provides the percent correct classification for each species (pct.correct), lower confidence intervals (LCI_0.95), upper confidence intervals (UCI_0.95), priors (expected error rate). Proximity plot (b) for species events from BANTER model (central dot color represents true species identity; color of circle surrounding dot represents BANTER species classification). Heat map (c) for ranks of variable importance for each species; colors scale from most important predictors (dark red) to least important predictors (dark blue). Vote Plot (d) shows the vote distribution for each event (vertical slice) for each species; distribution of votes by species is shown by their representative color. \]

@@

The most accurate model considered the echolocation clicks only (Detector Model: sampsize = 10, ntrees = 30,000; BANTER model: sampsize = 4, ntree = 200,000) and provided an overall correct classification rate of 89.7% for all four species. Classification scores ranged from a low of 82.1% (Cross Seamount Beaked Whale) to 96.7% (Longman's beaked whale, Fig. 3).  All classification results were greater than the expected error rate (Prior in Fig. 3a). Results from the EC model are presented here; results from EC_ICI model can be found in supplementary materials (Supplement Fig. 4).

@@

Rankin, S., and Archer, F., 2021. BANTER: A User\'s Guide to Acoustic Classification. https://taikisan21.github.io/PAMpal/banterGuide.html

@@

Rankin, S. and Barlow, J., 2005. Source of the North Pacific \"boing\" sound attributed to minke whales. J. Acoust. Soc. Am. 118(5), 3346-3351. https://doi.org/10.1121/1.2046747

Soldevilla, M.S., Henderson, E.E., Campbell, G.S., Wiggins, S.M., Hildebrand, J.A. and Roch, M.A., 2008. Classification of Risso\'s and Pacific white-sided dolphins using spectral properties of echolocation clicks. J. Acoust. Soc. Am. 124(1), 609-624. https://doi.org/10.1121/1.2932059

>>>>

  pdf: default

@@

      name: Ecological Informatics

@@

      model: 1p

@@

::: {layout="[[100,100], [100,100,100]]" layout-valign="bottom"}
|             | Chinstrap | Gentoo | Adelie | **% Correct** |
|-------------|-----------|--------|--------|---------------|
| Chinstrap   | 70        | 0      | 0      | 100.0         |
| Gentoo      | 0         | 5      | 0      | 100.0         |
| Adelie      | 0         | 0      | 65     | 100.0         |
| **Overall** | \-        | \-     | \-     | 100.0         |

| LCI 0.95 | UCI 0.95 | Prior |
|----------|----------|-------|
| 94.9     | 100.0    | 50.0  |
| 47.8     | 100.0    | 3.6   |
| 94.5     | 100.0    | 46.4  |
| 97.4     | 100.0    | 46.7  |

::: columns
a)  ![Fig.1](Figures/myplot1.jpg){#fig-1111}
:::

::: columns
b)  ![Fig.2](Figures/myplot2.jpg){#fig-2222}
:::

::: columns
c)  ![Fig.3](Figures/myplot3.jpg){#fig-3333}
:::

Figure 2. BANTER classification results from the SAtlantic dataset. Confusion matrix provides the percent correct classification for each species (pct.correct), lower confidence intervals (LCI_0.95), upper confidence intervals (UCI_0.95), priors (expected error rate). Proximity plot (a) for species events from BANTER model (central dot color represents true species identity; color of circle surrounding dot represents BANTER species classification). Heat map (b) for ranks of variable importance for each species; colors scale from most important predictors (dark red) to least important predictors (dark blue). Vote Plot (c) shows the vote distribution for each event (vertical slice) for each species; distribution of votes by species is shown by their representative color.
:::

@@

The most accurate model considered the echolocation clicks only (Detector Model: sampsize = 10, ntrees = 5,000; BANTER model: sampsize = 4, ntree = 10,000) and provided an overall correct classification rate of 91.8% for all four species. Classification scores ranged from a low of 84.5% (Cross Seamount Beaked Whale) to 97.5% (Longman's beaked whale, Fig. 3).  All classification results were greater than the expected error rate (Prior in Fig. 3a). Results from the EC model are presented here; results from EC_ICI model can be found in supplementary materials (Supplement Fig. 4).

::: kable(hawaii/hawaii_confuseMatrix) :::

::: columns
a)  [Fig.1](hawaii/hawaii_proximity.png)
:::

::: columns
b)  [Fig.2](hawaii/hawaii_importance.png)
:::

::: columns
c)  [Fig.3](hawaii/hawaii_votes.png)
:::

@@

Rankin, S., and Archer, F., 2021. BANTER: A User's Guide to Acoustic Classification. https://taikisan21.github.io/PAMpal/banterGuide.html

@@

Rankin, S. and Barlow, J., 2005. Source of the North Pacific "boing" sound attributed to minke whales. J. Acoust. Soc. Am. 118(5), 3346-3351. https://doi.org/10.1121/1.2046747

Soldevilla, M.S., Henderson, E.E., Campbell, G.S., Wiggins, S.M., Hildebrand, J.A. and Roch, M.A., 2008. Classification of Risso's and Pacific white-sided dolphins using spectral properties of echolocation clicks. J. Acoust. Soc. Am. 124(1), 609-624. https://doi.org/10.1121/1.2932059

### 2022-12-14 manuscript/manuscript.tex
Add Hawaii Dataset
Run Hawaii Dataset. Gitignore should include the binaries/database folders in the Hawaii folder dataset

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  authoryear,
  preprint,
  3p]{elsarticle}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[normalem]{ulem}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\journal{Journal Name}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Open-Source machine learning BANTER acoustic classification of a cryptic echolocating species},
  pdfauthor={Shannon Rankin; Taiki Sakai; Frederick Archer; Jay Barlow; Danielle Cholewiak; Annamaria DeAngelis; Jennifer L. K. McCullough; Erin Oleson; Melissa Soldevilla},
  pdfkeywords={bioacoustics, machine learning, random forest, species
classification, marine mammals, passive acoustic monitoring, beaked
whale},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\setlength{\parindent}{6pt}
\begin{document}

\begin{frontmatter}
\title{Open-Source machine learning BANTER acoustic classification of a
cryptic echolocating species}
\author[1]{Shannon Rankin%
\corref{cor1}%
\fnref{fn1}}
 \ead{shannon.rankin@noaa.gov} 
\author[1]{Taiki Sakai%
%
\fnref{fn2}}
 \ead{taiki.sakai@noaa.gov} 
\author[1]{Frederick Archer%
%
\fnref{fn3}}
 \ead{eric.archer@noaa.gov} 
\author[]{Jay Barlow%
%
}
 \ead{jaybarlow33@yahoo.com} 
\author[]{Danielle Cholewiak%
%
}
 \ead{danielle.cholewiak@noaa.gov} 
\author[]{Annamaria DeAngelis%
%
}
 \ead{annamaria.deangelis@noaa.gov} 
\author[]{Jennifer L. K. McCullough%
%
}
 \ead{jennifer.mccullough@noaa.gov} 
\author[]{Erin Oleson%
%
}
 \ead{erin.oleson@noaa.gov} 
\author[]{Melissa Soldevilla%
%
}
 \ead{melissa.soldevilla@noaa.gov}

\affiliation[1]{organization={Southwest Fisheries Science Center, Marine
Mammal \& Turtle Division},addressline={8901 La Jolla Shores
Dr.},city={La Jolla},postcode={92037},postcodesep={}}

\cortext[cor1]{Corresponding author}
\fntext[fn1]{This is the first author footnote.}
\fntext[fn2]{Another author footnote, this is a very long footnote and
it should be a really long footnote. But this footnote is not yet
sufficiently long enough to make two lines of footnote text.}
\fntext[fn3]{Yet another author footnote.}

\begin{abstract}
Passive acoustic monitoring is increasingly used for assessing
populations of marine mammals; however, analysis of large datasets is
limited by our ability to easily classify sounds detected.
Classification of beaked whale acoustic events, in particular, require
evaluation of multiple lines of evidence by expert analysts. Here we
present a highly automated approach to acoustic detection and
classification using supervised machine learning and open source
software methods. Data from four large scale surveys of beaked whales
(North Atlantic, South Atlantic, Hawaii, and Eastern Pacific) were
analyzed PAMGuard (acoustic detection), PAMpal (acoustic analysis) and
BANTER (hierarchical random forest classifier). Overall correct
classification results ranged from 86\% for the South Atlantic data to
99\% for the North Atlantic. Results for many species could likely be
improved with increased sample sizes and consideration of alternative
automated detectors. These methods provide a highly automated approach
to acoustic detection and classification using open source methods that
can be readily adopted for species and geographic regions.
\end{abstract}

\begin{keyword}
    bioacoustics \sep machine learning \sep random forest \sep species
classification \sep marine mammals \sep passive acoustic
monitoring \sep 
    beaked whale
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, boxrule=0pt, frame hidden, borderline west={3pt}{0pt}{shadecolor}, interior hidden, breakable, sharp corners]}{\end{tcolorbox}}\fi

@@

The most accurate model considered the echolocation clicks only
(Detector Model: sampsize = 10, ntrees = 30,000; BANTER model: sampsize
= 4, ntree = 200,000) and provided an overall correct classification
rate of 89.7\% for all four species. Classification scores ranged from a
low of 82.1\% (Cross Seamount Beaked Whale) to 96.7\% (Longman's beaked
whale, Fig. 3). ~All classification results were greater than the
expected error rate (Prior in Fig. 3a). Results from the EC model are
presented here; results from EC\_ICI model can be found in supplementary
materials (Supplement Fig. 4).

@@

Here are two sample references: \citet{Feynman1963118}
\citet{Dirac1953888}.

@@

  \bibliography{bibliography.bib}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[normalem]{ulem}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Open-Source machine learning BANTER acoustic classification of a cryptic echolocating species},
  pdfauthor={Shannon Rankin; Taiki Sakai; Frederick Archer; Jay Barlow; Danielle Cholewiak; Annamaria DeAngelis; Jennifer L. K. McCullough; Erin Oleson; Melissa Soldevilla},
  pdfkeywords={bioacoustics, machine learning, random forest, species
classification, marine mammals, passive acoustic monitoring, beaked
whale},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Open-Source machine learning BANTER acoustic classification of a
cryptic echolocating species}
\author{Shannon Rankin \and Taiki Sakai \and Frederick Archer \and Jay
Barlow \and Danielle Cholewiak \and Annamaria DeAngelis \and Jennifer L.
K. McCullough \and Erin Oleson \and Melissa Soldevilla}
\date{12/12/22}

\begin{document}
\maketitle
\begin{abstract}
Passive acoustic monitoring is increasingly used for assessing
populations of marine mammals; however, analysis of large datasets is
limited by our ability to easily classify sounds detected.
Classification of beaked whale acoustic events, in particular, require
evaluation of multiple lines of evidence by expert analysts. Here we
present a highly automated approach to acoustic detection and
classification using supervised machine learning and open source
software methods. Data from four large scale surveys of beaked whales
(North Atlantic, South Atlantic, Hawaii, and Eastern Pacific) were
analyzed PAMGuard (acoustic detection), PAMpal (acoustic analysis) and
BANTER (hierarchical random forest classifier). Overall correct
classification results ranged from 86\% for the South Atlantic data to
99\% for the North Atlantic. Results for many species could likely be
improved with increased sample sizes and consideration of alternative
automated detectors. These methods provide a highly automated approach
to acoustic detection and classification using open source methods that
can be readily adopted for species and geographic regions.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, sharp corners, borderline west={3pt}{0pt}{shadecolor}, interior hidden, breakable, enhanced, frame hidden]}{\end{tcolorbox}}\fi

@@

The most accurate model considered the echolocation clicks only
(Detector Model: sampsize = 10, ntrees = 5,000; BANTER model: sampsize =
4, ntree = 10,000) and provided an overall correct classification rate
of 91.8\% for all four species. Classification scores ranged from a low
of 84.5\% (Cross Seamount Beaked Whale) to 97.5\% (Longman's beaked
whale, Fig. 3). ~All classification results were greater than the
expected error rate (Prior in Fig. 3a). Results from the EC model are
presented here; results from EC\_ICI model can be found in supplementary
materials (Supplement Fig. 4).

::: kable(hawaii/hawaii\_confuseMatrix) :::

\begin{enumerate}
\def\labelenumi{\alph{enumi})}
\tightlist
\item
  \href{hawaii/hawaii_proximity.png}{Fig.1}
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\alph{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  \href{hawaii/hawaii_importance.png}{Fig.2}
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\alph{enumi})}
\setcounter{enumi}{2}
\tightlist
\item
  \href{hawaii/hawaii_votes.png}{Fig.3}
\end{enumerate}

@@

Here are two sample references: Feynman and Vernon Jr. (1963) Dirac
(1953).

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Dirac1953888}{}}%
Dirac, P. A. M. 1953. {``The {Lorentz} Transformation and Absolute
Time.''} \emph{Physica} 19 (1-\/--12): 888--96.
\url{https://doi.org/10.1016/S0031-8914(53)80099-6}.

\leavevmode\vadjust pre{\hypertarget{ref-Feynman1963118}{}}%
Feynman, R. P, and F. L Vernon Jr. 1963. {``The Theory of a General
Quantum System Interacting with a Linear Dissipative System.''}
\emph{Annals of Physics} 24: 118--73.
\url{https://doi.org/10.1016/0003-4916(63)90068-X}.

\end{CSLReferences}
